Fishing for Spam

### 2024-07-18 products/manuscript/Manuscript.qmd
Further exploration, prepping data for modeling, model tuning and multiple feature set iterations

---
title: "Fishing for Spam"
author: Sean O'Sullivan
date: "`r Sys.Date()`"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../../assets/dataanalysis-references.bib
csl: ../../assets/apa.csl
---

@@

I'd like to explore the features that are prevalent in the identification of spam emails. Utilizing text analysis, in addition to the other email attributes supplied and engineered, my end goal would be to model a classifier that has a high rate of efficacy in identifying spam emails for use of automated detection by some popular email providers and large internal IT departments across the corporate landscape.

>>>>

---
title: "Fishing for Spam"
subtitle: "Part 1: Project Proposal"
author: Sean O'Sullivan
date: "`r Sys.Date()`"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../../assets/dataanalysis-references.bib
csl: ../../assets/apa.csl
---

@@

I'd like to explore the features that are prevalent in the identification of spam emails. Utilizing text analysis in addition to the other email attributes supplied my end goal would be to model a classifier that has a high rate of efficacy in identifying spam emails for automated detection as used by some popular email providers and large internal IT departments across the corporate landscape.
